---
title: Pascal Schmidt's Resume"
author: Pascal Schmidt
date: "`r Sys.Date()`"
linkcolor: blue
output:
  pagedown::html_resume:
    css: ['css/custom_resume.css', 'css/styles.css', 'resume']
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)
library(tidyverse)
library(glue)

# Set this to true to have links turned into footnotes at the end of the document
PDF_EXPORT <- FALSE

# Holds all the links that were inserted for placement at the end
links <- c()

source('parsing_functions.R')


# First let's get the data, filtering to only the items tagged as
# Resume items
position_data <- read_csv('positions.csv') %>% 
  filter(in_resume) %>% 
  mutate(
    # Build some custom sections by collapsing others
    section = case_when(
      section %in% c('research_positions', 'industry_positions') ~ 'positions', 
      section %in% c('data_science_writings', 'by_me_press') ~ 'writings',
      TRUE ~ section
    )
  ) 

```


Aside
================================================================================

Contact {#contact}
--------------------------------------------------------------------------------

- <i class="fa fa-envelope"></i> pascal_schmidt@sfu.ca
- <i class="fa fa-mobile"></i> 778-686-2807
- <i class="fab fa-linkedin-in"></i> [Pascal-Schmidt](https://www.linkedin.com/in/pascal-data-science/)
- <i class="fa fa-github"></i> [Pascal-Schmidt](http://github.com/Pascal-SChmidt)
- <i class="fa fa-link"></i> [thatdatatho](http://thatdatatho.com)



Skills {#skills}
--------------------------------------------------------------------------------

- R/RStudio
- Shiny
- Markdown
- Power BI
- Python
- C++
- SQL 
- Version Control



Research {#Research}
--------------------------------------------------------------------------------

- [Molecular subtype not immune response drives outcomes in endometrial carcinoma]("https://clincancerres.aacrjournals.org/content/early/2018/12/06/1078-0432.CCR-18-3241")

Commonly Used Libraries for Projects and Work
------------------------------------------------

\n

- `tidyverse` (Data Cleaning)
- `caret` (Cross-validation, Machine Learning)
- `glmnet` (Lasso, Ridge)
- `Rcpp` (C++, for faster looping)

\n 

- `pandas` (Data Cleaning)
- `numpy` (Data Cleaning/Manipulation)
- `scikit-learn` (Machine Learning)


Main
================================================================================

Pascal Schmidt {#title}
--------------------------------------------------------------------------------

```{r}
intro_text <- "I recently graduated with a B.S. in Statistics, minor in Economics and have a keen interest in data science. This passion is reflected in my [personal blog](http://thatdatatho.com), Kaggle competitions, and hackathons. Outside of my academic pursuits, I am also an alumni of the SFU Men’s Soccer team."

cat(sanitize_links(intro_text))
```



Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

### B.S., Statistics, (Minor Economics)

Simon Fraser University	

Burnaby, BC

2014 - 2019		


Work Experience {data-icon=suitcase}
--------------------------------------------------------------------------------

### Data Science Co-op	

Statistics Canada	

Ottawa, ON	

May 2019 - August 2019	

- Developed functions for cleaning multiple data sets based on key criteria identified by our team and built the data set ready for analysis by using SQL join commands.	
- Created graphs and tables in `ggplot2` for a better understanding of why people's addresses on administrative data matches that on census data.	
- Modeled a logistic regression and interpreted the odds ratios for a better understanding of which predictors explain the reason of consistent addresses between admin data and census data. Project code can be found on my [github](https://github.com/Pascal-Schmidt/statistics-canada).	

### Data Science Trainee	

BC Cancer Agency	

Vancouver, BC	 

May 2018 - December 2018	

- Worked collaboratively on a meta-analysis of individual patient data to determine whether endometrial cancer patients need additional treatment.	
- Conducted exploratory data analysis by visualizing patterns and key characteristics for better insights and understanding of the data set.	
- Composed a bi-annual report by reshaping and joining multiple data sets, working extensively with R `tidyverse` packages such as `dplyr`, `ggplot2`, and `purrr`.	
- Developed graphs and tables for two clinical cancer
research papers, one published and one upcoming.

### R Tutor

Simon Fraser University

Burnaby, BC

September 2019 - Present

- Taught core `tidyverse` packages to students for an intuituve understanding of how these opinionated libraries work.
- Explained basic data structures, the fundamentals of programming, and best coding practices in order for students to gain comfort and speed with the R language.



Projects {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------

```{r}
print_section <- function(position_data, section_id){
  position_data %>% 
    filter(section == section_id) %>% 
    arrange(desc(end)) %>% 
    mutate(id = 1:n()) %>% 
    pivot_longer(
      starts_with('description'),
      names_to = 'description_num',
      values_to = 'description',
      values_drop_na = TRUE
    ) %>% 
    group_by(id) %>% 
    mutate(
      descriptions = list(description)
    ) %>% 
    ungroup() %>% 
    filter(description_num == 'description_1') %>% 
    mutate(
      timeline = ifelse(
        is.na(start) | start == end,
        end,
        glue('{end} - {start}')
      ),
      description_bullets = map_chr(descriptions, ~paste('-', ., collapse = '\n')),
    ) %>% 
    strip_links_from_cols(c('title', 'description_bullets')) %>% 
    mutate_all(~ifelse(is.na(.), 'N/A', .)) %>% 
    glue_data(
      "### {title}",
      "\n\n",
      "{description_bullets}",
      "\n\n\n",
    )
}

source('parsing_functions.R')
position_data %>% print_section('projects')
```