---
title: Pascal Schmidt's Resume"
author: Pascal Schmidt
date: "`r Sys.Date()`"
linkcolor: blue
output:
  pagedown::html_resume:
    css: ['css/custom_resume.css', 'css/styles.css', 'resume']
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)
library(tidyverse)
library(glue)

# Set this to true to have links turned into footnotes at the end of the document
PDF_EXPORT <- FALSE

# Holds all the links that were inserted for placement at the end
links <- c()

source('parsing_functions.R')


# First let's get the data, filtering to only the items tagged as
# Resume items
position_data <- read_csv('positions.csv') %>% 
  filter(in_resume) %>% 
  mutate(
    # Build some custom sections by collapsing others
    section = case_when(
      section %in% c('research_positions', 'industry_positions') ~ 'positions', 
      section %in% c('data_science_writings', 'by_me_press') ~ 'writings',
      TRUE ~ section
    )
  ) 

```


Aside
================================================================================

Contact {#contact}
--------------------------------------------------------------------------------

- <i class="fa fa-home"></i> 5391 McColl Crescent, Richmond, BC, V6V 2L6
- <i class="fa fa-envelope"></i> pascal_schmidt@sfu.ca
- <i class="fa fa-mobile"></i> 778-686-2807
- <i class="fab fa-linkedin-in"></i> [Pascal-Schmidt](https://www.linkedin.com/in/pascal-data-science/)
- <i class="fa fa-github"></i> [Pascal-Schmidt](http://github.com/Pascal-SChmidt)
- <i class="fa fa-link"></i> [thatdatatho](http://thatdatatho.com)



Skills {#skills}
--------------------------------------------------------------------------------

- R/RStudio
- Python
- C++
- SQL 
- Shiny
- Markdown
- Power BI
- Microsoft Excel
- Version Control (Git)
- Statistical Analysis


Research {#Research}
--------------------------------------------------------------------------------

- [Molecular subtype not immune response drives outcomes in endometrial carcinoma]("https://clincancerres.aacrjournals.org/content/early/2018/12/06/1078-0432.CCR-18-3241")

Commonly Used Libraries for Projects and Work
------------------------------------------------
<p> </p>
- <b> R: </b> 
- `tidyverse` (Data Cleaning)
- `caret` (Cross-validation, Machine Learning)
- `Rcpp` (C++, for faster looping)
- `glmnet` (Lasso, Ridge)
- `randomForest` (Machine Learning)
- `DBI`, `RSQLite` (Connect to databases, read in data from databases)


Main
================================================================================

Pascal Schmidt {#title}
--------------------------------------------------------------------------------

```{r}
intro_text <- "I recently graduated with a B.S. in Statistics, minor in Economics and have a keen interest in data science. This passion is reflected in my [personal blog](http://thatdatatho.com), Kaggle competitions, and hackathons. Outside of my academic pursuits, I am also an alumni of the SFU Men's Soccer team."

cat(sanitize_links(intro_text))
```



Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

### B.S., Statistics, (Minor Economics)

Simon Fraser University	

Burnaby, BC

2014 - 2019		


Work Experience {data-icon=suitcase}
--------------------------------------------------------------------------------

### Data Analyst (co-op)	

Statistics Canada	

Ottawa, ON	

May 2019 - August 2019	

- Developed R scripts for cleaning multiple data sets and used SQL join commands to built a final usable data set for analysis.	
- Built a R markdown report with tables and graphs for a better understanding of why people's addresses on administrative data matches that on census data.
- Created visualizations in Power BI to supplement the R markdown report.
- Feature engineered new variables for a better explanatory power of our logistic regression model. 
- Presented data and conclusions to my team, which used the results to gain actionable insights into the Census Program Transformation Project. Project code can be found on my [github](https://github.com/Pascal-Schmidt/statistics-canada).	

### Data Scientist (co-op)	

BC Cancer Agency	

Vancouver, BC	 

May 2018 - December 2018	

- Worked collaboratively on a meta-analysis of individual patient data to determine whether endometrial cancer patients need additional treatment.	
- Conducted an exploratory data analysis by visualizing patterns and key characteristics for better insights and understanding of the data set.	
- Composed a bi-annual report by cleaning, reshaping and joining multiple unstructured data sets, working extensively with R `tidyverse` packages such as `dplyr`, `purrr`, `tidyr`, and `stringr`. 	
- Independently researched and applied previously unkown statistical libraries for an improved data representation.  

### Data Analysis / R Tutor

Simon Fraser University

Burnaby, BC

January 2018 - Present

- Taught core `tidyverse` packages, data structures, the fundamentals of programming, and best coding practices to students. 
- Explained how to write basic queries in SQL to retrieve data from a database. 


Leadership Experience {data-icon=users}
--------------------------------------------------------------------------------

### Men's Soccer Varsity Team

Simon Fraser University

Burnaby, BC

September 2014 - April 2018

- Lead the team to two consecutive GNAC championships in 2016 and 2017.
- Won the GNAC Newcomer of the year award in 2015 through an exceptional soccer season with the SFU team.
- Mentored incoming freshman about the academic and athletic responsibilities of a student athlete. 

### Personal Blog

[thatdatatho.com](http://thatdatatho.com)

World

January 2018 - Present

- Published tutorials about various R libraries and other technical concepts such as web scraping, cross-validation, and machine learning algorithms.
- Explained specific R functions in detail by developing coding examples easily understandable by readers. 
- Helped commenters and other interested readers in becoming more familiar with statistical concepts and data cleaning tasks. 

Projects {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------

```{r}
print_section <- function(position_data, section_id){
  position_data %>% 
    filter(section == section_id) %>% 
    arrange(desc(end)) %>% 
    mutate(id = 1:n()) %>% 
    pivot_longer(
      starts_with('description'),
      names_to = 'description_num',
      values_to = 'description',
      values_drop_na = TRUE
    ) %>% 
    group_by(id) %>% 
    mutate(
      descriptions = list(description)
    ) %>% 
    ungroup() %>% 
    filter(description_num == 'description_1') %>% 
    mutate(
      timeline = ifelse(
        is.na(start) | start == end,
        end,
        glue('{end} - {start}')
      ),
      description_bullets = map_chr(descriptions, ~paste('-', ., collapse = '\n')),
    ) %>% 
    strip_links_from_cols(c('title', 'description_bullets')) %>% 
    mutate_all(~ifelse(is.na(.), 'N/A', .)) %>% 
    glue_data(
      "### {title}",
      "\n\n",
      "{description_bullets}",
      "\n\n\n",
    )
}

source('parsing_functions.R')
position_data %>% 
  print_section('projects')
```

Professional Development {data-icon=user-tie}
--------------------------------------------------------------------------------

```{r}
print_section <- function(position_data, section_id){
  position_data %>% 
    filter(section == section_id) %>% 
    arrange(desc(end)) %>% 
    mutate(id = 1:n()) %>% 
    pivot_longer(
      starts_with('description'),
      names_to = 'description_num',
      values_to = 'description',
      values_drop_na = TRUE
    ) %>% 
    group_by(id) %>% 
    mutate(
      descriptions = list(description)
    ) %>% 
    ungroup() %>% 
    filter(description_num == 'description_1') %>% 
    mutate(
      timeline = ifelse(
        is.na(start) | start == end,
        end,
        glue('{end} - {start}')
      ),
      description_bullets = map_chr(descriptions, ~paste('-', ., collapse = '\n')),
    ) %>% 
    strip_links_from_cols(c('title', 'description_bullets')) %>% 
    mutate_all(~ifelse(is.na(.), 'N/A', .)) %>% 
    glue_data(
      "### {title}",
      "\n\n",
      "{description_bullets}",
      "\n\n\n",
    )
}

source('parsing_functions.R')
position_data %>% 
  print_section('development')
```

```{css, echo=FALSE}
/* Remove the fake bullets from lists */
.extra-sidebar li::before {
  content: auto;
}

/* Dont put the little fake list point in front of links */
.extra-sidebar li::before {
  display: none;
}

/* Move closer to start and up towards header */
.extra-sidebar ul {
  padding-left: 1rem;
}

.extra-sidebar li::before {
  position: relative;
  margin-left: -4.25pt;
  content: "• ";
}

/* Make sure elements in asside are centered and have a nice small text */
.extra-sidebar {
  width: calc(var(--sidebar-width) + 9px);
  line-height: 1.5;
  font-size: 0.75rem;
}

.extra-sidebar {
  height: 100%;
  width: var(--sidebar-width) !important;
  padding-left: 0.75rem;
  padding-right: 0;
  padding-top: 2rem;;
}

.extra-sidebar h1 {
  display: none;
}

.extra-sidebar .level2:first-of-type {
  margin-top: 0;
}

.extra-sidebar p {
  margin-block-start: 0.75em;
  margin-block-end: 0;
}
```

Second page sidebar {.aside .extra-sidebar}
================================================================================

<p></p>
<p></p>
- <b> Python:  </b>
- `pandas` (Data Cleaning)
- `numpy` (Data Cleaning/Manipulation)
- `scikit-learn` (Machine Learning)

<p></p>
<p></p>

Hackathon
---------------------------------------------------------

-  <b> 2017 VANSASH:
Vancouver Sports Analytics Symposium & Hackathon </b>
<p></p>

- In a team of 4, analyzed ice hockey data provided by the Vancouver Canucks.
<p></p>
- Predicted where most goals are scored from by extracting stops from power plays. 
<p></p>
- Identified key players on the ice through visualizations using the `ggplot2` package.
<p></p>
- Presented our findings and visualization in front of a judging panel and 60 other participants.

Interests
------------------------------------------------

- Soccer
<p></p>
- Table Tennis
<p></p>
- Skiing
<p></p>
- Hiking
<p></p>
- Reading
<p></p>
- Travel